Adopting agile software development in the large organizations: A systematic literature review

### 2014-05-26 journal/article.tex
Work in progress

@@

@@

Even if any activities aiming for transformation can be considered as
investments in themselves, the transformation process included investments in
some tangible entities. These investments were focused on enabling agile
software development. Typical investments were new management tools,
improvements in testing environments, and updating of the physical working
spaces.

>>>>

Even if any activities aiming for transformation can be considered as
investments in themselves, the transformation process included investments in
some tangible entities. These investments were focused on enabling agile
software development. Typical investments were new management tools,
improvements in testing environments, and updating of the physical working
spaces. Table \ref{table:transformation_investments} summarizes the

\begin{table}
    \centering
    \begin{tabular}{ >{\raggedright\arraybackslash}p{0.51\textwidth}
                     >{\raggedright\arraybackslash}p{0.41\textwidth} }
        Investment for transformation      &  Described in  \\
        \midrule
        Proprietary agile material or documentation   & 
                P1, P2, P8, P14, P16, P23, P26, P29, P31, P32, P41, P45  \\
        \bottomrule
    \end{tabular}
    \caption{Activities in the organization aiming to create change}
    \label{table:transformation_investments}
\end{table}

@@

P: In-house agile material or documentation

P 1: Abdelnour-Nocera 2007 - Adopting Agile in a large organization - balancing the old with the new.pdf - 1:9 [A key tool which formed part o..]  (7:2069-7:2717)   (Super)
Codes:	[P: In-house agile material or documentation - Family: Practices] 
No memos

A key tool which formed part of this group’s TF was a manual of agile adoption 
which was generated by this group. However, it was not designed to carry agile 
methods beyond software engineering, i.e. into the wider business environment. There 
was one document we saw being circulated at mid-management level which contained 
some principles to make the whole of the business agile. According to one of the 
stakeholders, this was intended to provide guidance in “getting rid of old projects and 
keeping new ones”. The logic for this is that “other parts of the new business need to 
be agile also for the agile adoption to be successful”.

Comment:
This group is the agile advocates and coaches.

P 2: Abdelnour-Nocera 2008 - Adopting Agile In A Large Organisation.pdf - 2:10 [A key tool was a manual of agi..]  (5:2063-5:2242)   (Super)
Codes:	[P: In-house agile material or documentation - Family: Practices] 
No memos

A key 
tool was a manual of agile adoption generated by this group, but it was not designed 
to carry agile methods beyond software engineering, i.e. to the business environment.

P 8: Brown 2011 - A Case Study In Agile-At-Scale Delivery.pdf - 8:14 [The customization and packagin..]  (6:624-6:1113)   (Super)
Codes:	[P: In-house agile material or documentation - Family: Practices] 
No memos

The customization and packaging of the agile 
delivery process for ABC Bank was given its own identity (including a logo, 
graphics, posters, and so on). This encapsulated the specific choices of concepts, 
processes, and terminology for agile delivery and both expressed them in a 
vocabulary that was familiar, and also made them more readily identifiable to the 
wide range of stakeholders around ABC Bank that would be involved with the 
enterprise software delivery organization.

P14: Fecarotta 2008 - Myboeingfleet And Agile Software Development.pdf - 14:12 [It has been about six months s..]  (3:3330-3:3548)   (Super)
Codes:	[P: In-house agile material or documentation - Family: Practices] 
No memos

It has been about six months since this approval.  
Ryan’s team has created the Agile AD&S website 
using a wiki, which encourages participation, and 
emphasizes the openness and collaborative nature of 
the effort.

P16: Fry 2007 - Large Scale Agile Transformation In An On-Demand World.pdf - 16:8 [One team member wrote a docume..]  (2:1312-2:1852)   (Super)
Codes:	[P: In-house agile material or documentation - Family: Practices] [S: Communicating the change - Family: RQ4: Success factors] [S: Engage people broadly in the organization - Family: RQ4: Success factors] 
No memos

One team member wrote a document describing the
new process, its benefits and why we were
transitioning from the old process. We led 45 one-hour
meetings with key people from all levels in the
organization. Feedback from these meetings was
incorporated into the document after each meeting,
molding the design of the new process and creating
broad organizational buy-in for change. This open
communication feedback loop allowed everyone to
participate in the design ofthe new process and engage
as an active voice in the solution.

P16: Fry 2007 - Large Scale Agile Transformation In An On-Demand World.pdf - 16:14 [Three key members from the cro..]  (2:3195-2:3413)   (Super)
Codes:	[P: In-house agile material or documentation - Family: Practices] 
No memos

Three key members from the cross-functional
team developed a consolidated presentation and
training deck that included concepts from the current
methodology, Scrum [1], XP (eXtreme Programming)
and Lean methods [2].

P16: Fry 2007 - Large Scale Agile Transformation In An On-Demand World.pdf - 16:16 [We also created an internal, w..]  (2:3602-2:3775)   (Super)
Codes:	[P: In-house agile material or documentation - Family: Practices] 
No memos

We
also created an internal, wiki-based website as a
repository for all our information and as a valuable
reference for team members transitioning to the new
methodology.

P23: Hanly 2006 - Agile Coaching In British Telecom - Making Strawberry Jam.pdf - 23:11 [It was clear that people would..]  (2:3889-2:4172)   (Super)
Codes:	[P: In-house agile material or documentation - Family: Practices] 
No memos

It was clear that people would need a quick and 
easy way of finding out about Agile Delivery and how 
it was to be applied in BT. The BT Agile Cookbook – 
an online collection of wisdom, guidance and advice 
on Agile Delivery as applied to BT – was developed to 
meet the need.

P23: Hanly 2006 - Agile Coaching In British Telecom - Making Strawberry Jam.pdf - 23:13 [BT’s cookbook describes Agile ..]  (3:1-3:313)   (Super)
Codes:	[P: In-house agile material or documentation - Family: Practices] 
No memos

BT’s cookbook describes Agile Delivery in terms of 
its traditional software development roles: the 
customer, project manager, business analyst, designer, 
developer and tester. It describes what's different and 
why, and it sets out the agile core practices which are 
seen as giving BT Exact most benefit.

P26: Laanti 2008 - Implementing Program Model With Agile Principles In A Large Software Development Organization.pdf - 26:8 [All these new practices were i..]  (3:132-3:216)   (Super)
Codes:	[P: In-house agile material or documentation - Family: Practices] 
No memos

All these new practices were institutionalized with the 
Agile Policy (Appendix A).

P27: Lee 2008 - Forming To Performing - Transitioning Large-Scale Project Into Agile.pdf - 27:9 [In each phase, we encountered ..]  (2:78-2:330)   (Super)
Codes:	[P: In-house agile material or documentation - Family: Practices] [S: Pilot program provides knowledge of transformation - Family: RQ4: Success factors] 
No memos

In each phase, we encountered different sets of
problems and we came up with creative tricks to solve
them. The solutions evolved into “better or best
practices”. These techniques shared within our team
and were then adopted by the whole department.

P29: Lewis 2007 - Over The Waterfall In A Barrel - Msit Adventures In Scrum.pdf - 29:6 [The first task became mapping ..]  (1:3088-1:3554)   (Super)
Codes:	[P: In-house agile material or documentation - Family: Practices] 
No memos

The first task became mapping waterfall terms 
with Scrum terms.  Pre-Baseline became one of the 
“Phase-end reviews” and Business Requirements 
Document (BRD) became Product Backlog, captured 
at the start of each Sprint.   
Once terms were defined, an Agile SDLC Guide 
was written.  This document describes Scrum in 
terms common to the SDLC and included such topics 
as “What is Agile?”, “What is Scrum?” and “How 
does the MS IT SDLC differ from Scrum?”

P31: Maples 2009 - Enterprise Agile Transformation - The Two-Year Wall.pdf - 31:22 [When we first embarked on our ..]  (6:918-6:1469)   (Super)
Codes:	[I: Inhouse coaching resources - Family: Investing in change] [P: In-house agile material or documentation - Family: Practices] [S: Change leaders or champions - Family: RQ4: Success factors] 
No memos

When we first embarked on our Agile journey, we 
made the decision to hire an Agile expert to serve as 
our Agile evangelist and “guidance counselor.”  This 
person has been with Borland since the very start of 
our transformation, and he established “Borland Agile” 
– the baseline process and framework for our entire 
organization. His role is very much to guide, coach and 
mentor all of the teams and to ensure that as we scale 
and evolve, the adaptations we make to the Scrum 
practices never take us too far away from the 
principles.

P32: McDowell 2007 - British Telecom Experience Report - Agile Intervention - Bt'S Joining The Dots Events For Organizational Change.pdf - 32:9 [The key content pieces address..]  (5:1963-5:2633)   (Super)
Codes:	[P: In-house agile material or documentation - Family: Practices] 
No memos

The key content pieces address highest impact opportunities for change.  This involves agile planning and estimation (which infers iterative delivery and user stories), 
customer collaboration (a current gap with business partner involvement inside the 
delivery cycle) and inter/intra-team communication (how to ensure good communication with distributed teams).  Short, nine minute videos have been created in each area 
to provide a uniform delivery of information.  While these videos are run by agile 
coaches, the video format both ensures that every participant receives the same content as well as lessening the burden of having highly experienced presenters.

P41: Roche 2009 - The Amazing Team Race A Team Based Agile Adoption.pdf - 41:13 [Increase competencies to devel..]  (2:992-2:1272)   (Super)
Codes:	[P: In-house agile material or documentation - Family: Practices] [S: A successful agile (pilot) project at the beginning - Family: RQ4: Success factors] 
No memos

Increase competencies to develop high 
performing teams.  Ultimately we knew 
establishing well-run Scrum teams would 
determine the success of the adoption. We wanted 
to showcase these teams, identify and share their 
practices so that their successes could be 
duplicated.

P41: Roche 2009 - The Amazing Team Race A Team Based Agile Adoption.pdf - 41:22 [The community used the newslet..]  (3:439-3:621)   (Super)
Codes:	[P: In-house agile material or documentation - Family: Practices] [S: Communicating the change - Family: RQ4: Success factors] [S: Have an agile community - Family: RQ4: Success factors] 
No memos

The community used the newsletters 
to keep up to date on the transition effort; goals of 
the transition team, upcoming Scrum events, 
interesting articles and Scrum trivia games.

P45: Schnitter 2011 - Large-Scale Agile Software Development At Sap Ag.pdf - 45:13 [A wiki was used to manage basi..]  (4:55-4:667)   (Super)
Codes:	[P: In-house agile material or documentation - Family: Practices] [P: SIG's, CoP's - Family: Practices] 
No memos

A wiki was used to manage basic information and observations. For each pilot team
the following data were collected by the Scrum mentors: scope of the project, duration,
product owner, scrum master, dependencies with other teams, locality, critical decisions
and impediments, and other observations. These data were used to select and communicate best practices, create a network of Scrum masters and product owners, and set
up a round table of experienced practicioners. In-depth interviews with Scrum masters,
product owners, and team members provided valuable information and suggestions for
improvement.

@@
